Supplementary material

### 2022-11-13 submission/supplement.rmd
add sensitivity analyses

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: true
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  - \newcommand\given[1][]{\:#1\vert\:}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

@@

# Simulation settings
For all patients we observe covariates $x_1,\dots,x_8$, of which $4$ are
continuous and $4$ are binary. More specifically,

\begin{equation*}
x_1,\dots,x_4 \sim N(0, 1)
\end{equation*}
\begin{equation*}
x_5,\dots,x_8 \sim B(1, 0.2)
\end{equation*}

We first, generate the binary outcomes $y$ for the untreated patients ($t_x=0$),
based on

\begin{equation} 
P(y\given \bm{x}, t_x=0) = g(\beta_0 + \beta_1x_1+\dots+\beta_8x_8) = g(lp_0),
(\#eq:p0)
\end{equation}

@@

\begin{equation}
P(y\given\bm{x}, t_x=1) = g(lp_1)
(\#eq:p1)
\end{equation}

@@

## Base-case scenario
The base-case scenario assumes a constant odds ratio of $0.8$ in favor of
treatment. The simulated datasets are of size $n=4250$, where treatment is
allocated at random using a 50/50 split (80% power for the detection of an
unadjusted OR of 0.8, assuming an event rate of 20% in the untreated
arm). Outcome incidence in the untreated population is set at $20\%$. For the
development of the prediction model we use the model defined in \@ref(eq:p0)
including a constant treatment effect. When doing predictions, $t_x$ is set to
$0$. The value of the true $\bm{\beta}$ is such that the above prediction model
has an AUC of $0.75$.

The previously defined targets are achieved when $\bm{\beta}=(-2.08,
0.49,\dots,0.49)^t$. For the derivations in the treatment arm we use
$\bm{\gamma}=(\log(0.8), 1, 0)^t$.

@@

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
asd <- read_csv(
  here("data/processed/analysisIds.csv")
) %>%
  select(-"type")
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  caption     = "Scenario settings of the entire simulation study.",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c",
    "Before harms",
    "After harms"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 3,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4,
      "Benefit"               = 2
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

@@

```{r, cache=TRUE, echo=FALSE, fig.cap="Simulation scenarios that closely follow trials. In this case, we see increasing absolute benefits with increasing baseline risk.", fig.show="hold", out.width = '50%'}
include_graphics(
  c(
    here("figures/scenario_251.png"),
    here("figures/scenario_324.png")
  )
)
```

```{r, cache=TRUE, echo=FALSE, fig.cap="Simulation scenarios that closely follow trials. In this case, we see increasing absolute benefits with increasing baseline risk up to the third risk quarter. In the fourth risk quarter this trend is interrupted and benefits are diminished.", fig.show="hold", out.width = '50%'}
include_graphics(
  c(
    here("figures/scenario_406.png"),
    here("figures/scenario_422.png")
  )
)
```

@@

\begin{equation}
P(y=1\given\bm{x}, t_x) = g(\bm{x}^t\bm{\beta} + \gamma t_x)
\end{equation}
(\#eq:risk)

The risk linear predictor is then 
$lp(\bm{x}; \bm{\beta}) = \bm{x}^t\bm{\beta}$. 
We derive baseline risk predictions for patients by setting $t_x=0$ in
\@ref(eq:risk). All methods for individualizing benefit predictions are 2-stage
methods, that start by fitting a model for predicting baseline risk. The
estimated linear predictor of this model is

\begin{equation*}
\hat{lp} = lp(\bm{x};\hat{\bm{\beta}}) = \bm{x}^t\hat{\bm{\beta}}
\end{equation*}

@@

## Constant treatment effect
Assuming a constant relative treatment effect, fit the adjusted model in
\@ref(eq:risk). Then, an estimate of absolute benefit can be derived from
$$\tau(lp;  \hat{\bm{\beta}}, \hat{\gamma}) = g(\hat{lp}) - g(\hat{lp}+\hat{\gamma}) $$

## Linear interaction
The assumption of constant relative treatment effect is relaxed modeling a
linear interaction of treatment with the risk linear predictor:

$$P(y=1\given lp, t_x;\hat{\bm{\beta}}) = g(\delta_0 + \delta_1\hat{lp} +
\gamma_0t_x + \gamma_1\hat{lp}t_x)$$

Then the predicted absolute benefit is 
$$\tau(lp;\hat{\bm{\beta}},\bm{\gamma}, \bm{\delta}) = g(\delta_0 +
\delta_1\hat{lp}) - g\big((\delta_0+\gamma_0) + (\delta_1+\gamma_1)\hat{lp}\big)$$

## Restricted cubic splines
Finally, we drop the linearity assumption and predict absolute benefit using
smoothing with restricted cubic splines with $k=3, 4$ and $5$ knots. More
specifically, we fit the model:

$$P(y=1|lp, t_x;\hat{\bm{\beta}}, \bm{\delta}, f_{RCS}) = g\big(\delta_0 + \gamma
t_x +f_{RCS}(\hat{lp})\times t_x\big)$$
where
$$f_{RCS}(x)=\alpha_0+\alpha_1h_1(x)+\alpha_2h_2(x)+\dots+\alpha_{k-1}h_{k-1}(x)$$
with $h_1(x)=x$ and for $j=2,\dots,k-2$
$$h_{j+1}(x)= (x-t_j)^3-(x-t_{k-1})_+^3 \frac{t_k-t_j}{t_k-t_{k-1}}+(x-t_k)^3_+\frac{t_{k-1}-t_j}{t_k-t_{k-1}}$$
where 
$t_1,\dots,t_k$ are the selected knots. We predict absolute benefit from 
$$ \tau(lp; \hat{\bm{\beta}}, \delta_0, f_{RCS}) = P(y=1\given\hat{lp},
t_x=0) - P(y=1\given \hat{lp}, t_x=1) $$

@@

\newpage
# Discrimination and calibration for benefit

@@

We carried out a smaller set of simulations, in which we assumed true
treatment-covariate interactions. Sample size was set to 4,250 and the AUC of
the true prediction model was set to 0.75. The following scenarios were
considered: 1) 4 true weak positive interactions
($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=0.83$); 2) 4 strong positive
interactions ($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=0.61$); 3) 2 weak and 2
strong positive interactions; 4) 4 weak negative interactions 
($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=1.17$); 5) 4 strong negative interactions 
($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=1.39$); 6) 2 weak and 2 strong negative
interactions; 7) combined positive and negative strong interactions. We also
considered constant treatment-related harms applied on the absolute scale to all
treated patients. The exact settings were: 1) absent treatment-related harms; 2)
moderate treatment-related harms, defined as 25\% of the average true benefit of the
scenario without treatment-related harms; 3) strong treatment-related harms
defined as 50\% of the true average benefit of the scenario without
treatment-related harms; 4) negative treatment-related harms (benefit), defined
as an absolute risk reduction for treated patients of 50\% of the true average
benefit of the scenario without treatment-related harms. The exact settings can
be found in Table \@ref(tab:tab2).

```{r tab2, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
asd <- read_csv(
  here("data/processed/analysisIdsInteractions.csv")
)
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable = TRUE,
  align = "r",
  booktabs = TRUE,
  caption = "Scenario settings of the treatment-covariate interaction scenarios.",
  col.names = c(
    "Scenario",
    "Base",
    "Type",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    "g0", "g1", "g2", "g5", "g6",
    "Before harms",
    "After harms"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 5,
      "Benefit"               = 2
      )
  ) %>%
  kableExtra::kable_styling(font_size = 6)
```

@@

>>>>

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: true
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  - \newcommand\given[1][]{\:#1\vert\:}
  - \newcommand{\indep}{\perp \!\!\! \perp}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

@@

# Notation
We observe RCT data $(Z, X, Y)$, where for each patient $Z_i= 0, 1$ is the
treatment status, $Y_i = 0, 1$ is the observed outcome and $X_i$ is a set of
covariates measured. Let $\{Y_i(z), z=0, 1\}$ denote the unobservable potential
outcomes. We observe $Y_i = Z_iY_i(1) + (1 - Z_i)Y_i(0)$. We are interested in
predicting the conditional average treatment effect (CATE), 
$$\tau(x) = E\{Y(0) - Y(1)|X=x\}$$ 
Assuming that $(Z, X, Y)$ is a random sample from the target population and that
$\big(Y(0), Y(1)\big)\indep Z|X$, as we are in the RCT setting, we can predict
CATE from
\begin{align*}
\tau(x) &= E\{Y(0)\given X=x\}-E\{Y(1)\given X=x\}\\
&=E\{Y\given X=x, Z=0\}-E\{Y\given X=x, Z=1\}
\end{align*}

Based on an estimate of baseline risk
$$
E\{Y\given X=x, Z=0\}=g\big(\hat{lp}(x)\big)
$$
with $\hat{u}=\hat{lp}(x)=x^t\hat{\beta}$ the linear predictor and $g$ the link function,
we predict CATE from
$$
\hat{\tau}(x) = g\big(f(\hat{u}, 0)\big) - g\big(f(\hat{u}, 1)\big)
$$
where $f(u,z)$ describes interactions of the baseline risk linear predictor with
treatment.

# Simulation settings
For all patients we observe covariates $X_1,\dots,X_8$, of which $4$ are
continuous and $4$ are binary. More specifically,

\begin{equation*}
X_1,\dots,X_4 \sim N(0, 1)
\end{equation*}
\begin{equation*}
X_5,\dots,X_8 \sim B(1, 0.2)
\end{equation*}

We first, generate the binary outcomes $Y$ for the untreated patients ($Z=0$),
based on

\begin{equation} 
P(Y(0)=1\given X=x) = g(\beta_0 + \beta_1x_1+\dots+\beta_8x_8) = g(lp_0),
(\#eq:p0)
\end{equation}

@@

\begin{equation}
P(Y = 1\given X=x, Z=1) = g(lp_1)
(\#eq:p1)
\end{equation}

@@

## Base-case scenario
The base-case scenario assumes a constant odds ratio of $0.8$ in favor of
treatment. The simulated datasets are of size $n=4250$, where treatment is
allocated at random using a 50/50 split (80% power for the detection of an
unadjusted OR of 0.8, assuming an event rate of 20% in the untreated
arm). Outcome incidence in the untreated population is set at $20\%$. For the
development of the prediction model we use the model defined in \@ref(eq:p0)
including a constant treatment effect. When doing predictions, $Z$ is set to
$0$. The value of the true $\beta$ is such that the above prediction model
has an AUC of $0.75$.

The previously defined targets are achieved when $\beta=(-2.08,
0.49,\dots,0.49)^t$. For the derivations in the treatment arm we use
$\gamma=(\log(0.8), 1, 0)^t$.

@@

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
asd <- read_csv(
  here("data/processed/analysisIds.csv")
) %>%
  select(-c("type", "averageTrueBenefit", "averageObservedBenefit"))
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "rlrrlr",
  booktabs    = TRUE,
  caption     = "Scenario settings of the entire simulation study.",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 3,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

@@

```{r, cache=TRUE, echo=FALSE, warning=FALSE, fig.cap="Simulation scenarios that closely follow trials. In this case, we see increasing absolute benefits with increasing baseline risk.", fig.show="hold", out.width = '50%'}
include_graphics(
  c(
    here("figures/scenario_251.png"),
    here("figures/scenario_324.png")
  )
)
```

```{r, cache=TRUE, echo=FALSE, warning = FALSE, fig.cap="Simulation scenarios that closely follow trials. In this case, we see increasing absolute benefits with increasing baseline risk up to the third risk quarter. In the fourth risk quarter this trend is interrupted and benefits are diminished.", fig.show="hold", out.width = '50%'}
include_graphics(
  c(
    here("figures/scenario_406.png"),
    here("figures/scenario_422.png")
  )
)
```

@@

\begin{equation}
P(Y=1\given X=x,Z=z) = g(x^t\beta + \delta_0 z)
\end{equation}
(\#eq:risk)

We derive baseline risk predictions for patients by setting $Z=0$ in
\@ref(eq:risk). All methods for individualizing benefit predictions are 2-stage
methods, that start by fitting a model for predicting baseline risk. The
estimated linear predictor of this model is

\begin{equation*}
\hat{lp} = lp(x;\hat{\beta}) = x^t\hat{\beta}
\end{equation*}

@@

## Constant treatment effect
Assuming a constant relative treatment effect, fit the adjusted model in
\@ref(eq:risk). Then, predict absolute benefit using

\begin{equation}
\hat{\tau}(x;\hat{\beta},\hat{\gamma})=g(f(\hat{lp}, 0)) - g(f(\hat{lp},1)), 
(\#eq:main)
\end{equation}

where $f(\hat{lp}, z) = \hat{lp}+\hat{\delta}_0z$, with $\hat{\delta}_0$ the
estimated relative treatment effect (log odds ratio).

## Linear interaction
We relax the assumption of a constant relative treatment effect in
\@ref(eq:main) by setting

$$ f(\hat{lp}, z) = \delta_0+\delta_1z+\delta_2\hat{lp}+\delta_3z\hat{lp} $$

## Restricted cubic splines
Finally, we drop the linearity assumption and predict absolute benefit using
smoothing with restricted cubic splines with $k=3, 4$ and $5$ knots. More
specifically, we set:

$$ f(\hat{lp}, z) = \delta_0 + \delta_1z+zs(\hat{lp}) $$
where
$$s(x)=\alpha_0+\alpha_1h_1(x)+\alpha_2h_2(x)+\dots+\alpha_{k-1}h_{k-1}(x)$$
with $h_1(x)=x$ and for $j=2,\dots,k-2$
$$h_{j+1}(x)= (x-t_j)^3-(x-t_{k-1})_+^3 \frac{t_k-t_j}{t_k-t_{k-1}}+(x-t_k)^3_+\frac{t_{k-1}-t_j}{t_k-t_{k-1}}$$
where 
$t_1,\dots,t_k$ are the selected knots [@harrell2017regression].

@@

\newpage
# Discrimination and calibration for benefit
The c-for-benefit represents the probability that from two randomly chosen
matched patient pairs with unequal observed benefit, the pair with greater
observed benefit also has a higher predicted benefit. To be able to calculate
observed benefit, patients in each treatment arm are ranked based on their
predicted benefit and then matched 1:1 across treatment arms. Observed treatment
benefit is defined as the difference of observed outcomes between the untreated
and the treated patient of each matched patient pair. Predicted benefit is
defined as the average of predicted benefit within each matched patient pair.

We evaluated calibration in a similar manner, using the integrated calibration
index (ICI) for benefit [@Austin2019]. The observed benefits are regressed on the
predicted benefits using a locally weighted scatterplot smoother (loess). The
ICI-for-benefit is the average absolute difference between predicted and smooth
observed benefit. Values closer to represent better calibration.

@@

We carried out a smaller set of simulations, in which we assumed true
treatment-covariate interactions. Sample size was set to 4,250 and the AUC of
the true prediction model was set to 0.75. The following scenarios were
considered: 1) 4 true weak positive interactions
($\text{OR}_{Z=1} / \text{OR}_{Z=0}=0.83$); 2) 4 strong positive
interactions ($\text{OR}_{Z=1} / \text{OR}_{Z=0}=0.61$); 3) 2 weak and 2
strong positive interactions; 4) 4 weak negative interactions 
($\text{OR}_{Z=1} / \text{OR}_{Z=0}=1.17$); 5) 4 strong negative interactions 
($\text{OR}_{Z=1} / \text{OR}_{Z=0}=1.39$); 6) 2 weak and 2 strong negative
interactions; 7) combined positive and negative strong interactions. We also
considered constant treatment-related harms applied on the absolute scale to all
treated patients. The exact settings were: 1) absent treatment-related harms; 2)
moderate treatment-related harms, defined as 25\% of the average true benefit of the
scenario without treatment-related harms; 3) strong treatment-related harms
defined as 50\% of the true average benefit of the scenario without
treatment-related harms; 4) negative treatment-related harms (benefit), defined
as an absolute risk reduction for treated patients of 50\% of the true average
benefit of the scenario without treatment-related harms. The exact settings can
be found in Table \@ref(tab:tab2).

```{r tab2, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
asd <- read_csv(
  here("data/processed/analysisIdsInteractions.csv")
) %>%
  select(-c("averageTrueBenefit", "averageObservedBenefit"))
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable = TRUE,
  align = "rllrrlr",
  booktabs = TRUE,
  caption = "Scenario settings of the treatment-covariate interaction scenarios.",
  col.names = c(
    "Scenario",
    "Base",
    "Type",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    "g0", "g1", "g2", "g5", "g6"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 6,
      "Baseline risk"         = 9,
      "True treatment effect" = 5
      )
  ) %>%
  kableExtra::kable_styling(font_size = 6)
```

@@

\newpage

# Correlated covariates

We analyzed the sensitivity of our results to correlation between baseline
characteristics by incuding additional simulation scenarios. We sampled
covariates $W_1,\dots,W_8\sim N(0, \Sigma)$. We generated four continuous
baseline covariates $X_1=W_1,\dots,X_4=W_4$ and four binary covariates with 20\%
prevalence $X_5=I(W_5>z_{0.8}), X_8=I(W_8>z_{0.8})$, where $I$ is the indicator
function. We selected the covariance matrix $\Sigma$ such that
$\text{cor}(X_i,X_j)=0.5$, for any $i\neq j$. More precisely, we set $\Sigma$ as
can be seen below:

\begin{equation*}
\Sigma = 
\begin{pmatrix}
1       & 0.5   & 0.5   & 0.5   & 0.708 & 0.708 & 0.708 & 0.708 \\
0.5     & 1     & 0.5   & 0.5   & 0.708 & 0.708 & 0.708 & 0.708 \\
0.5     & 0.5   & 1     & 0.5   & 0.708 & 0.708 & 0.708 & 0.708 \\
0.5     & 0.5   & 0.5   & 1     & 0.708 & 0.708 & 0.708 & 0.708 \\
0.708   & 0.708 & 0.708 & 0.708 & 1     & 0.745 & 0.745 & 0.745 \\
0.708   & 0.708 & 0.708 & 0.708 & 0.745 & 1     & 0.745 & 0.745 \\
0.708   & 0.708 & 0.708 & 0.708 & 0.745 & 0.745 & 1     & 0.745 \\
0.708   & 0.708 & 0.708 & 0.708 & 0.745 & 0.745 & 0.745 & 1
\end{pmatrix}
\end{equation*}

In order to ensure that the simulated datasets were comparable to the original
main simulation scenarios, i.e. control arm event rate of 20\% and true risk
model c-statistic (AUC) equal to the target, we needed to adjust the
coefficients of the true risk model. The exact settings of the simlation
scenarios for the sensitivity analyses can be found in Table \@ref(tab:tab3).

```{r tab3, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
asd <- read_csv(
  here("data/processed/analysisIdsSensitivity.csv")
) %>%
  select(-c("type", "averageTrueBenefit", "averageObservedBenefit"))
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "rlrrlr",
  booktabs    = TRUE,
  caption     = "Scenario settings of the entire simulation study.",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 3,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

The results of the sensitivity analyses can be explored in Figures ... We found
no noticeable differences between methods for individualizing treatment benefit
predictions compared to the results of the simulation scenarios where baseline
covariates were assumed to be statistically independent.

```{r rmseBaseSensitivity, cache=TRUE, echo=FALSE, fig.cap="RMSE of the sensitivity analyses assuming correlated baseline covariates. All considered methods were derived using simulated samples of size 4,250 and true prediction c-statistic of 0.75", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_moderate_base_sensitivity.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseSampleSizeSensitivity, cache=TRUE, echo=FALSE, fig.cap="RMSE of the sensitivity analyses assuming correlated baseline covariates. All considered methods were derived using simulated samples of size 17,000 and true prediction c-statistic of 0.75", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_moderate_sample_size_sensitivity.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r rmseAucSensitivity, cache=TRUE, echo=FALSE, fig.cap="RMSE of the sensitivity analyses assuming correlated baseline covariates. All considered methods were derived using simulated samples of size 4,250 and true prediction c-statistic of 0.85", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_moderate_auc_sensitivity.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
